Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-24 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added FDS Images to Figures Dstar  update bib

In Chapter 2 the fires from the burners were characterized.  In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.  The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will compared.  Two burner positions are examined, 0.61~m from the wall and 0.0~m from the instrumented gypsum wallboard wall.

@@

>>>>

In Chapter 2 the fires from the burners were characterized.  In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.  The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will be compared.  Then the data generated from the instrumented gypsum wallboard fires are compared with results from FDS simulations.  Four burner positions are examined, beginning 0.61~m from the wall to moving to 0.0~m, where one edge of the burner is in contact with the instrumented gypsum wallboard wall.  First the the plume data will be examined based on the size of the computational grid cells used in the FDS simulations.

@@

Choosing the size of the grid when performing an amalysis with FDS is critical. In studies where large rooms or portions of buildings have been involved grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Vettori:2000,Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.

 A measure of how well the flow field is resolved is given by the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell. This value has been referred to as the plume resolution index. Given that the fire plume region is the focus of this study, it is important to understand how changes in plume mesh resolution impact the results.

\begin{equation}
 D^* = \left(
     \frac{\dot Q}{\rho_\infty  c_p  T_\infty  \sqrt{g} }
     \right)^\frac{2}{5} 
 \end{equation}

The characteristic fire diameter is defined by the relationship of the characteristic fire size to the physical diameter of the fire, ${Q^*} = ({D^*}/{D})^{5/2}$, where $D$ is the physical diameter of the fire. The quantity, $\dot Q$, is the total heat release rate of the fire. The quantity $({D^*}/{\delta x})$ is approximately the number of computational grid cells that span the characteristic diameter of the fire ~\cite{FDS_Users_Guide,FDS_Validation_Guide}.

Computational grid cell sizes of 80~mm, 40~mm, and 20~mm where used in FDS to model the fire.  The resulting plume resolutions were approximately 4.4, 8.8, and 17.5 respectively. Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.  Figure~ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons
